A multi-scale story of the diffusion of a new technology: the web

### 2025-01-03 paper/submission2/response.qmd

> The text from these webpages was scanned using a regular expression
(regex) to identify strings of text which resemble UK postcodes and one
fifth of them included a mention to a postcode [@BL2013geo]. This
information allows the geolocation of the data and the creation of the
LAD and OA counts. To prevent false positives, the resulted postcodes
were matched against official postcode lookup files [@ons].

\noindent 2. Then, to remove the bias from link farms associated with a handful of postcodes
having irregular high numbers of websites pointing to them, a targeted data 
imputation procedure was developed. This is detailed in the data section -- see
also Figure 1.

\noindent 3. Regarding the points about subsidiary company location and event postings, 
these cannot be directly observed and distinguished. However, a process that has 
been successfully used in previous studies has been adopted here. Firstly, given 
that the focus of the paper is commercial websites, the relevant literature 
illustrates that such websites serve specific purposes:

> they are used to diffuse information, support online transactions and share 
opinions [@THELWALL2000441; @blazquez2018big].

Secondly, the webpage-to-website aggregation process leads to websites with 
different number of postcodes as presented in Table 1. To decrease heterogeneity, 
the analysis firstly focuses on websites with one unique postcode. Given the the
commercial nature of these websites (.co.uk), it is fair to expect that such 
websites with one unique postcode in their web text represent companies with a 
single trading location. The analysis included in the main body of the paper is
based on this subset of the website population. For year 2000, this includes 
70% of all the archived, geolocated commercial websites. Then, as a robustness
check all the different steps of the analysis are repeated for websites with up 
to 10 postcodes and the results are presented in the appendix. This includes 94%
of all the archived, geolocated commercial websites. For this step, websites 
with multiple postcodes were counted multiple times, one for each different 
postcode. All the results are qualitatively the same and only marginally 
different, which is indication of the robustness of the website geolocation 
strategy.

As a further argument for the robustness of the above process, the results of a 
previous study which used the same approach for a small subset of these data 
from a specific neighbourhood in London matched in terms of accuracy previous 
research that was based on extensive qualitative work, interviews and 
observational studies [@shoreditch]. This last point has now been added in the 
relevant section:

> Previous research which used the same methodology for a small subset of these 
data illustrates the robustness of the above approach: its results matched in 
terms of accuracy past rounds of research based on extensive qualitative work, 
interviews and observational studies for the same study area [@shoreditch].

\color{teal}
\noindent 3. Equation 2: The rationale behind Equation 2 is unclear. Shouldn’t the primary predictor of website density at time tbe the location density at t-1? Why was this approach chosen over a growth model? Additionally, clarify how spatial dependencies are accounted for in the model.
\color{black}

**growth as an appendix, spatial dependencies have been included**

\color{teal}
\noindent 5. Results\
\noindent 1. Diffusion Speed: The decision to binarize diffusion speed is questionable. Continuous measures, such as growth rates or the time required to reach 50% saturation, would provide more informative insights.
\color{black}

**This is only for the map, this is a critical point in diffusion studies**

\color{teal}
\noindent 2. Geographical Scale: While the effort to model diffusion curves at a fine geographical scale is commendable, the paper does not sufficiently explain the benefits or additional knowledge gained from this approach.
\color{black}

**reveal that theories are valid for lcoal scales and inform local tech policies**

\color{teal}
\noindent 3. Early Adopters and Latecomers: The discussion of early-adopter and latecomer advantages is underdeveloped. How do these advantages manifest locally? What specific benefits arise if a company registers its website six months earlier than competitors in other locations? If this aspect is retained, it should be elaborated in the theory section, including how it relates to local capabilities or diffusion hierarchies.
\color{black}

**relates to local capabilities or diffusion hierarchies**

\color{teal}
\noindent 4. Descriptive Statistics: The value of the descriptive Moran’s I and Gini coefficient analyses in Section 4.2 is unclear. Instead, calculating growth rates of adoption and examining their distribution over time would offer a better sense of adoption speed and magnitude.
\color{black}

**think, growth rates will not work for OA**

\color{teal}
\noindent 5. Retail Centers: The sudden shift to retail centers on page 15 is confusing, given that the data pertains to all commercial sites. Clarify the rationale for this focus.
\color{black}

**hierarchy**

\color{teal}
\noindent 6. Modeling Details: The methodological details in Section 4.3 should be moved to the methods section to maintain clarity and coherence. Including these details in the results section is confusing.
\color{black}

\color{teal}
\noindent 7. Clarity and Structure: Section 4.3 is difficult to follow. Clearly state the main message and highlight how diffusion mechanisms vary spatially. Develop hypotheses to structure the results and provide potential explanations for observed heterogeneity. Without this, the section feels like a descriptive summary without clear takeaways for the reader.
\color{black}

\color{teal}
\noindent 
Overall Recommendations
\noindent 1. Consistency: Ensure consistent terminology and focus throughout the paper, particularly when referring to the web and commercial websites.
\noindent 2. Structure: Adopt a clearer structure by separating the introduction, theory/literature review, methods, and results sections.
\noindent 3. Clarity: Develop hypotheses to frame the results and provide clearer explanations for methodological choices and findings.
\color{black}

## References
